The Fates of Merging Supermassive Black Holes and A Proposal for a New Class of X-Ray Sources

### 2019-11-15 paper.tex
Final edits before sending to certain references for opinions

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.}
\label{fig:meosmbh}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/q_merger_fraction.png}
\caption{Fraction of BHs that merge with the central BH as a function of the BH mass ratio.  Each point represents the fraction of galaxy mergers that led to BH mergers for each BH merger ratio bin.  Note that a "bin" at each point is comprised of the mass ratio at that point up to, but not including, the next point on the x-axis.}
\label{fig:q_merge_fraction}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/time_to_merge.png}
\caption{Time required for BHs to merge with host SMBH after galaxy merger.}
\label{fig:time_to_merge}
\end{center}
\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/kicked_stats.png}
\caption{Histogram of kicked and not-kicked SMBHs at z=0.}
\label{fig:kicked_stats}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
\caption{Final Radii of remaining orbital black holes at z=0}
\label{fig:mvr}
\end{center}
\end{figure}

@@

%\begin{figure}[ht]
%\begin{center}
%\includegraphics[width=0.45\%textwidth]{plots/"Final %Luminosities of Orbiting %BHs".png}
%\caption{Luminosities of %Orbiting BHs at z=0}
%\label{fig:loobhs}
%\end{center}
%\end{figure}

\begin{figure}[ht]
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"luminosities_final".png}
\caption{Luminosity of orbiting BHs at z=0 as per Inayoshi (2019).}
\label{fig:loobhs}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Summary Results All Galaxies".png}
\caption{Histogram of merged, ejected, and orbiting SMBHs at z=0 as a function of BH mass.  Colored arrows along x-axis represent median masses of respective sets.}
\label{fig:meosmbh}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/q_merger_fraction.png}
\caption{Fraction of BHs that merge with the central BH as a function of the BH mass ratio.  Each point represents the fraction of galaxy mergers that led to BH mergers for each BH merger ratio bin.  Note that a "bin" at each point is comprised of the mass ratio at that point up to, but not including, the next point on the x-axis.}
\label{fig:q_merge_fraction}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/time_to_merge.png}
\caption{Time required for BHs to merge with host SMBH after galaxy merger.  Form for fitted line is $-0.379M_{BH}+5.766$ in log-log space.}
\label{fig:time_to_merge}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/kicked_stats.png}
\caption{Histogram of kicked and not-kicked SMBHs at z=0.  Colored arrows along x-axis represent median masses of respective sets.}
\label{fig:kicked_stats}
\end{center}
\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"Final Radius v Mass of Orbiting BHs".png}
\caption{Final Radii of remaining orbital black holes at z=0.}
\label{fig:mvr}
\end{center}
\end{figure}

@@

%\begin{figure}
%\begin{center}
%\includegraphics[width=0.45\%textwidth]{plots/"Final %Luminosities of Orbiting %BHs".png}
%\caption{Luminosities of %Orbiting BHs at z=0}
%\label{fig:loobhs}
%\end{center}
%\end{figure}

\begin{figure}
\begin{center}
\includegraphics[width=0.5\textwidth]{plots/"luminosities_final".png}
\caption{Luminosity of orbiting BHs at z=0 as per Inayoshi (2019).}
\label{fig:loobhs}
\end{center}
\end{figure}
